Tables/Graphs for Article

### 2018-01-03 article/draft1.Rnw
combined univariate results tables

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction, and increase web traffic. This paper presents a survival analysis of response time, or the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

Community-driven online question and answer forums (CQA) are becoming widely-used sources of information. These online platforms feature thousands of user-posted questions and answers, and can receive millions of visits every month. The CQA analyzed in this paper is iFixit's \textit{Answers} forum. Founded in 2003, iFixit's mission is to equip users with the knowledge and tools to repair their broken devices, as part of an effort to save money and reduce electronic waste. This company provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.

As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is another important resource. This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered iPhone screens and faulty vehicle air conditioners, with over 100,000 solutions. As thousands of users rely on this forum for information, it is important that users receive timely answers. Fast response times enhance user experience and increase web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum. Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times, and for how the forum design can be improved.

@@

With the recent increase in the popularity and use of CQAs, these platforms have been the subject of a multitude of studies related to information sciences. Regarding analysis of response times, \cite{Bhat2014} developed a classification model to estimate response times for questions posted on \textit{Stack Overflow}, using both tag-based and textual features. Analysis determine that tag-based features, like the number of ``popular'' tags a question contains or the number of users subscribed to a tag, were the best predictors of response time. \cite{Mahmud} proposed models based on exponential distributions to predict response times, and were built from users' previous wait times for responses. \cite{Rechavi2011} analyzed response times and satisfaction rates for questions posted on \textit{Yahoo Answers!}, and determined that the fastest times were between users who did not follow each other, while the longest times were between users who were mutual friends in the social network. \cite{Asaduzzaman2013} developed a taxonomy for classifying unanswered questions on \textit{Stack Overflow}, and developed a model to predict how long a question would remain unanswered using textual features like title and post length and whether or not the question contained code, and user features, like the number of questions asked and answered by the user prior to posting. The analysis presented in this paper seeks to analyze response time through survival analysis methods, methods that have not yet been investigated or applied to CQAs.

The majority of existing research has been focused on predicting question and answer quality by using both textual and non-textual features of posts. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com}, using primarily textual features (surface, lexical, syntactic, forum-specific, and similarity (relatedness of a post to the topic of the forum) features). \cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate metric of Wikipedia article quality. Wikipedia articles can represent the same kind of user-generated content featured on CQAs. On the other hand, \cite{H.fu} found that non-textual features, like revision and comment count on an answer or the number of points or merit badges a user has, were the most useful indicators of answer quality across four different knowledge domains on \textit{Stack Exchange}. A number of other studies have also developed classification algorithms using both textual and non-textual features with the similar goal of predicting question and answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a}. \cite{Ravi2014} presented a slightly different approach by analyzing the content of posts and utilizing latent topic models to predict quality. \cite{Anderson2012} developed models to the long term value of a question and its answers on \textit{Stack Overflow}. The present analysis combines both textual and non-textual features of questions on iFixit's \textit{Answers} forum in a Cox regression model to predict survival probability of questions.

@@

% Table of categorical predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Day of the week the question was posted \\ \hline
  Device category the question pertains to. Categories include: Android\/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \hline
  Whether or not the question's text contains any end punctuation marks (. ? !) \\ \hline
  Whether or not the question's text is in all lower case \\ \hline
  Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See appendix for a complete list of these terms. \\ \hline
  Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See appendix for a complete list of these terms. \\ \hline
  Whether or not the question's title ends in a question mark \\ \hline
  Whether or not the user edited or added information to the question's text sometime after posting it \\ \hline
  Whether or not the user made an effort to solve the problem prior to asking the question \\ \hline
\end{tabular}
\caption{Categorical predictors derived}
\label{table:categorical}
\end{table}

@@

The data analyzed contained 8,025 questions posted from April 8, 2017 (10:14 PM) to July 7, 2017 (9:28 PM) (the date the data was downloaded). Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time when the question was posted, and date and time when the first answer was received. Variables derived can be found in Table \ref{table:categorical} and \ref{table:continuous}. See appendix for information on how predictors were created.

@@

Questions analyzed were restricted to those posted in English. The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the times in the data (questions can still receive answers after the download date) \cite{Kleinbaum2011}.

Survival was defined as the event that a question did not receive an answer beyond a certain time, t. Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \cite{Bland1998}. From these estimates, survival curves were constructed to examine the survival experience of questions. Mean, median and other percentiles of survival times were also generated.

As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}. To build the model, five-fold cross-validation was used \cite{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}. Each predictor was entered into univarite Cox models, and strength of association with response times was assessed. Those with partial likelihood ratio test p-values of less than 0.001 were included in the final model. Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include into the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}. All predictors found to be signficant, along with the transformations and functional forms found to be necessary, were included in the model for cross-validation. No variable selection was used, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than leaving all predictors in.

In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time. The resulting Nagelkerke's R-square statistic, concordance statistic, Somers' Dxy, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}. Signficant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with all predictors, and the log partial likelihood function for the null model with no predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the X2 distribution \cite{find}. Concordance statistics and Somers' Dxy are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard ratio. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' Dxy is the difference between the model's concordance statistic and discordance, 0.5. A Somers' Dxy statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

@@

To obtain predicted survival probabilities using the model, the predictSurvProb function was used from the pec package. This function uses the Cox model and a vector of times to compute predicted survival probabilities.

@@

% Univariate analysis on quantitative predictors
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
  Predictor & p-value \\ 
  \hline \hline
  *Log transformation of the number of characters in a question's text & 0.00 \\ \hline
  *Square root transformation of the number of characters in a question's text & 1.1102e-16 \\ \hline
  Number of characters in a question's text (untransformed) & 6.9472e-12 \\\hline
  *Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text & 1.1488e-11 \\ \hline
  *Square root transformation of the average frequency ``score'' of a question's tags & 1.4642e-11 \\ \hline
  Average frequency ``score'' of a question's tags (untransformed) & 1.2706e-08 \\ \hline
  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 1.3988e-7 \\ \hline
  *Square root transformation of the number of characters in the user-defined device title & 2.2914e-4 \\ \hline
  *Square root transformation of the average number of characters in a question's tags & 2.9999e-4 \\ \hline
  Number of characters in the user-defined device title (untransformed) & 6.5304e-3 \\ \hline
  Average number of characters in a question's tags (untransformed) & 2.6115e-2 \\ \hline
\end{tabular}
\label{table:qresults}
\end{table}

% Univariate analysis on categorical predictors
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for categorical predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
 Predictor & p-value \\ 
  \hline \hline
  Day of the week the question was posted & 7.8677e-4 \\ \hline
  Device category & 0.00 \\ \hline
  Whether or not the question's text contained at least one end punctuation mark & 2.5354e-9 \\ \hline
  Whether or not the question's text is in all lower case & 1.5400e-7 \\ \hline
  Whether or not the question's title contains terms considered to be frequently used among answered questions & 7.6397e-5 \\ \hline
  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ \hline
  Whether or not the question's title ended in a questionmark & 1.1423e-12 \\ \hline
  Whether or not the user edited or added information to the question's text sometime after posting it & 2.5472e-7 \\ \hline
  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ \hline
  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 3.1648e-5 \\ \hline

\end{tabular}
\label{table:cresults}
\end{table}

% Univariate analysis on quantitative predictors
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
\begin{tabular}{| p{5cm} | l | l |}
  \hline
  Predictor & Transformation & p-value \\ 
  \hline
  \multirow{3}{5cm}{Average number of characters in each questions tags}
  & Untransformed & 2.6115e-2 \\ 
  & Log & NA \\
  & Square root & 2.9999e-4 \\ \hline
  \multirow{3}{5cm}{Average frequency score of a question’s tags}
  & Untransformed & 1.2706e-08 \\
  & Log & NA \\
  & Square root & 1.4642e-11 \\ \hline
  \multirow{3}{5cm}{Number of characters in a question's text}
  & Untransformed & 6.9472e-12 \\
  & Log & 0.00 \\
  & Square root & 1.1102e-16 \\ \hline
  \multirow{3}{5cm}{Number of characters in the user-defined device title}
  & Untransformed & 6.5304e-3 \\
  & Log & NA \\
  & Square root & 2.2914e-4 \\ \hline
  \multirow{3}{5cm}{Ratio of the number of line breaks to the number of characters in a question's text} 
  & Untransformed & 1.3988e-7 \\
  & Log & NA \\
  & Square root & 1.1488e-11 \\ \hline
\end{tabular}
\label{table:qresults}
\end{table}

@@

Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions. Results of univariate analysis, performed on one training set, for transformed and untransformed continuous predictors, and every categorical predictor, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively. All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.

>>>>

Community-driven online question and answer forums (CQA) contain an expansive amount of crowd-sourced knowledge. Thousands of questions and answers are posted everyday. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. A reliable measure of the health of these CQAs is question response time. Fast response times enhance user engagement and satisfaction and increase web traffic. This paper presents a survival analysis of the time until a question receives its first answer. A Cox proportional hazards model was developed to predict the survival probability of a question, or the probability that a question receives an answer before a certain time. Though several predictors were signficant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies can investigate if factors identified as signifcant in this analysis can be generalized to other CQAs.

@@

Community-driven online question and answer forums (CQA) are becoming widely-used sources of information. These online platforms feature thousands of user-posted questions and answers and can receive millions of visits every month. The CQA analyzed in this paper is iFixit's \textit{Answers} forum. Founded in 2003, iFixit's mission is to equip users with the knowledge and tools to repair their broken devices, as part of an effort to save money and reduce electronic waste. This company provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.

As not all possible repairs are covered in the published guides and users may have additional questions related to existing guides, iFixit's \textit{Answers} forum is an important resource for users. This platform features questions pertaining to over 9,000 devices, ranging from jammed zippers to shattered iPhone screens and faulty vehicle air conditioners, with over 100,000 solutions. As thousands of users rely on this forum for information, it is important that users receive timely answers. Fast response times enhance user experience and increase web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum. Analysis of response times can reveal factors that affect how quickly questions receive answers, which can lead to suggestions for how users can ask better questions to minimize response times, and for how the forum design can be improved.

@@

With the recent increase in the popularity and use of CQAs, these platforms have been the subject of a multitude of studies related to information sciences. Regarding analysis of response times, \cite{Bhat2014} developed a classification model to estimate response times for questions posted on \textit{Stack Overflow}, using both tag-based and textual features. Analysis determine that tag-based features, like the number of ``popular'' tags a question contains or the number of users subscribed to a tag, were the best predictors of response time. \cite{Mahmud2013} proposed models based on exponential distributions to predict response times, and were built from users' previous wait times for responses.  Both \cite{Bhat2014} and \cite{Mahmud2013} restrict analysis to questions for which the response time is observed, ignoring unanswered questions; meanwhile \cite{Asaduzzaman2013} focused exclusively on characteristics of unanswered questions. \cite{Asaduzzaman2013} developed a taxonomy for classifying unanswered questions on \textit{Stack Overflow}, and developed a model to predict how long a question would remain unanswered using textual features like title and post length, and user features like the number of questions asked and answered by the user prior to posting. The research presented in this paper uses the framework of survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

The majority of existing research has been focused on predicting question and answer quality by using both textual and non-textual features of posts. \cite{Weimer2007} developed a classification algorithm to assess the quality of posts on \textit{Nabble.com}, using primarily textual features (surface, lexical, syntactic, forum-specific, and similarity (relatedness of a post to the topic of the forum) features). \cite{Blumenstock} also determined that textual features, i.e word count, was the most accurate metric of Wikipedia article quality. Wikipedia articles can represent the same kind of user-generated content featured on CQAs. On the other hand, \cite{H.fu} found that non-textual features, like revision and comment count on an answer or the number of points or merit badges a user has, were the most useful indicators of answer quality across four different knowledge domains on \textit{Stack Exchange}. A number of other studies have also developed classification algorithms using both textual and non-textual features with the similar goal of predicting question and answer quality \cite{Yao2015} \cite{Toba2014} \cite{Ponzanelli2014a}. \cite{Ravi2014} presented a slightly different approach by analyzing the content of posts and utilizing latent topic models to predict quality. \cite{Anderson2012} developed models to the predict the long term value of a question and its answers on \textit{Stack Overflow}. The present analysis combines both textual and non-textual features of questions on iFixit's \textit{Answers} forum in a Cox regression model to predict survival probability of questions.

@@

% Table of categorical predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Day of the week the question was posted \\ \hline
  Device category the question pertains to. Categories include: Android\/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \hline
  Whether or not the question's text contains any end punctuation marks (. ? !) \\ \hline
  Whether or not the question's text is in all lower case \\ \hline
  Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See Appendix for a complete list of these terms. \\ \hline
  Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See Appendix for a complete list of these terms. \\ \hline
  Whether or not the question's title ends in a question mark \\ \hline
  Whether or not the user edited or added information to the question's text sometime after posting it. \\ \hline
  Whether or not the user made an effort to solve the problem prior to asking the question. \\ \hline
\end{tabular}
\caption{Categorical predictors derived}
\label{table:categorical}
\end{table}

@@

The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (the date the data was downloaded). Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time when the question was posted, and date and time when the first answer was received. Variables derived can be found in Table \ref{table:categorical} and \ref{table:continuous}. See Appendix for more details on variable derivation.

@@

Questions analyzed were restricted to those posted in English. The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \cite{Kleinbaum2011}.

Survival was defined as the event that a question did not receive an answer beyond a certain time, \textit{t}. Estimates of survival probability were generated with the Kaplan-Meier method, which adjusts to the presence of right-censored, or unanswered questions \cite{Bland1998}. From these estimates, survival curves were constructed to examine the survival experience of questions. Mean, median and other percentiles of survival times were also generated.

As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}. To build the model, five-fold cross-validation was used \cite{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}. Each predictor was entered into univarite Cox models, and strength of association with response times was assessed. Those with partial likelihood ratio test p-values of less than 0.001 were included in the final model. Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include into the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}. All predictors found to be signficant, along with the transformations and functional forms found to be necessary, were included in the model for cross-validation. No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than including all predictors.

In each fold of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time. The resulting Nagelkerke's R-square statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}. Signficant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with all predictors, and the log partial likelihood function for the null model with no predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the $Ichi^2$ distribution \cite{find}. Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard ratio. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5. A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

@@

To obtain predicted survival probabilities using the model, the \textit{predictSurvProb} function was used from the pec package. This function uses the Cox model and a vector of times to compute predicted survival probabilities.

@@

% Univariate analysis results
\begin{table}[!htbp]
\centering
\caption{Univariate analysis results for continuous predictors, ordered by increasing p-values} 
\begin{tabular}{| p{5cm} | p{2.5cm} | p{2cm} |}
  \hline
  Predictor & Transformation & p-value \\ 
  \hline
  \multirow{ 3 }{ 5cm }{ Average frequency score of a question's tags }
  & Untransformed & 1.270620e-08 \\
  & Log + 1 & 1.186521e-08 \\
  & *Square root & 1.464184e-11 \\ \hline
  \multirow{ 3 }{ 5cm }{ Average number of characters in each question's tags }
  & Untransformed & 2.611529e-02 \\ 
  & *Log + 1 & 6.018542e-05 \\
  & Square root & 2.999917e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Number of characters in a question's text }
  & Untransformed & 6.947221e-12 \\
  & *Log & 0.000000e+00 \\
  & Square root & 1.110223e-16 \\ \hline
  \multirow{ 3 }{ 5cm }{ Number of characters in the user-defined device title }
  & Untransformed & 6.530431e-03 \\
  & *Log + 1 & 1.912977e-05 \\
  & Square root & 2.291424e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Ratio of the number of line breaks to the number of characters in a question's text } 
  & Untransformed & 1.398819e-07 \\
  & Log + 1 & 1.092952e-07 \\
  & *Square root & 1.148792e-11 \\ \hline
  \multicolumn{ 2 }{ |l| }{ *Day of the week the question was posted } & 7.867705e-04 \\ \hline
  \multicolumn{ 2 }{ |l| }{ *Device category } & 0.000000e+00 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ *Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
  \multicolumn{2}{| p{7.5cm}|}{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.5cm}| }{ *Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
\end{tabular}
\label{table:univariate_results}
\end{table}

@@

Each training set contained \Sexpr{nrow(train1)} questions, and each test set contained \Sexpr{nrow(test1)} questions. Results of univariate analysis, performed on one training set, are shown in Table \ref{table:univariate_results}. All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.
